Exploring Constraint Grammar as a SAT problem

### 2015-03-30 paper/nodalida2015.tex
squeezing a bit

\paragraph{Rules are unordered.}
A typical CG rule sequence starts with rules that are either very common, or have a complex condition to fulfil.
Stronger rules appear towards the end, to be applied if none of the weaker rules has. 
%For a rule set such as following, this order is crucial:

@@

To replace the sequential order, we have experimented with different strategies:
\begin{itemize}
\item Maximise number of rules used---We discarded this strategy, because it was too strong: if a rule leads to a conflict in one case, it was not be applied anywhere.
\item Emulate sequential order---Enter clauses produced by each rule one by one, and assume the solver state reached so far is correct; if a conflict is introduced by new clauses, discard them and move on to next.
\item [\checkmark] Maximise number of rule applications---If there is a conflict, find the smallest number of rule applications to discard so that the conflict is solved.
\end{itemize}

@@

@@

The heuristics worked with examples in the order of tens of rules, but moving to hundreds of rules, the rules interact more, the results are more mixed. 
Rule sets in order of thousands of rules remains to be tested.

@@

\begin{table}
  \centering
  \begin{tabular}{|l|l|c|c|}
     \hline
	        \textbf{Text} & \textbf{\# words, rules} &  \textbf{SATCG} & \textbf{VISLCG3} \\ \hline
    \multirow{2}{*}{\textbf{Don Quijote}} & 186460 words  &  2m53.7s & 10.7s \\ 
		                                           & 261 rules & & \\ \hline
    \multirow{2}{*}{\textbf{Pride and}}  & 153386 words& 55.7s  & 4.8s \\ 
                         {\textbf{Prejudice}}                   & 99 rules & \\ \hline
  \end{tabular}
  \caption{Comparing execution times between SATCG and VISLCG3.}
  \label{table:time}
\end{table}

>>>>

\paragraph{Rules are unordered.}
%A typical CG rule sequence starts with rules that are either very common, or have a complex %condition to fulfil.
%Stronger rules appear towards the end, to be applied if none of the weaker rules has. 
%For a rule set such as following, this order is crucial:

@@

%To replace the sequential order, 
We have experimented with different strategies:
\begin{itemize}
\item Maximise number of rules used---We discarded this strategy, because it was too strong: if a rule leads to a conflict in one case, it was not be applied anywhere.
\item Emulate sequential order---Enter clauses produced by each rule one by one, and assume the solver state reached so far is correct; if a conflict is introduced by new clauses, discard them and move on to next.
\item [\checkmark] Maximise number of rule applications---If there is a conflict, find the smallest number of rule applications to discard so that the conflict is solved.
\end{itemize}

@@

The chosen heuristic produced the best results with examples in the order of tens or hundreds of rules.
Larger rule sets (thousands of rules) are yet to be tested.

@@

@@

\begin{table}
  \centering
  \begin{tabular}{|l|l|c|c|}
     \hline
   \textbf{\# words} & \textbf{\# rules} &  \textbf{SATCG} & \textbf{VISLCG3} \\ \hline
              153,386    & 99    & 55.7s     & 4.8s \\  %\hline
                186,460  & 261  &  2m53.7s & 10.7s \\\hline
  \end{tabular}
  \caption{Execution times.}
  \label{table:time}
\end{table}
